VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_eval.tex
re

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achives a 85K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achives 20K:1 (10GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increses to about 220MB. 
Notice that the sampled index method is designed for single-machine deduplication.
%and it is not easy to extend to a distributed cluster architecture.

@@

{\bf Memory usage with multi-VM processing and disk bandwidth with  I/O throttling}. 
We have further studied the memory and disk bandwidth usage 
when running concurrent VM snapshot backup on each machine with $\sigma=2\%$. 
Table ~\ref{tab:resource_usage} gives the resource usage  when
running 1 or multiple  VM backup tasks at the same time on each physical machine. 
Each task handles the backup of one VM snapshop including deduplication.
``CPU'' column is the percentage of a single core used. 
``Mem'' column includes $\sim$100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
recipe metadata and cache. 
The ``Read'' column is controlled to 50MB/s local disk bandwidth usage with I/O throttling so that other 
cloud services are not significantly impacted.
The peak raw storage read performance is about 300MB/s and we only use 16.7\% with this collocation consideration.
``Write'' is the I/O write usage of QFS; note that each QFS write triggers disk writes in multiple machines due to
data replication.     50MB/s dirty segment read speed triggers about 16.4MB/s disk write for non duplicates with one backup task.
% [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
% the cloud infrastructure services and are shared among many applications.]
%We see our hybrid deduplication scheme only occupies a small amount of system resources. 
%The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
%memory during duplicate detection.

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of software layers
when I/O throttling is not applied to control usage. The
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
Column ``QFS'' is the write request traffic to the underlying file system after compression.
For example, with 148 MB/s write traffic to the snapshot store, QFS write traffic is about 35.3 MB/s
after compression.  However, the underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46 GB/s 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset, each version of total snapshots has abut 1TB per machine for 25 VMs and  thus  each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
In comparison, the sampled index method in~\cite{Guo2011} achives about 5.5GB per second
with 16 concurrent backup tasks and 6GB per second with
more tasks.  Thus the per-machine throughput of our scheme is reasonable.
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

@@

We demonstrate  the impact of adding extra replication for PDS in VC
and compare the snapshot availability of VC and VO. 
Appendix~\ref{sect:fault} provides a detailed analysis of 
snapshot availablility and the estimated result depends on how frequent a duplicate chunk
is shared among snapshots of VMs.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO 
and VC approaches
and then calculate the average availability of VM snapshots.

>>>>

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achieves a 85K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achieves 20K:1 (10GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increases to about 220MB. 
Notice that the sampled index method is designed for single-machine deduplication.
%and it is not easy to extend to a distributed cluster architecture.

@@

{\bf Memory usage with multi-VM processing and disk bandwidth with  I/O throttling}. 
We have further studied the memory and disk bandwidth usage 
when running concurrent VM snapshot backup on each machine with $\sigma=2\%$. 
Table ~\ref{tab:resource_usage} gives the resource usage  when
running 1 or multiple  VM backup tasks at the same time on each physical machine. 
Each task handles the backup of one VM snapshot including deduplication.
``CPU'' column is the percentage of a single core used. 
``Mem'' column includes $\sim$100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
recipe metadata and cache. 
The ``Read'' column is controlled to 50MB/s local disk bandwidth usage with I/O throttling so that other 
cloud services are not significantly impacted.
The peak raw storage read performance is about 300MB/s and we only use 16.7\% with this collocation consideration.
``Write'' is the I/O write usage of QFS; note that each QFS write triggers disk writes in multiple machines due to
data replication.     50MB/s dirty segment read speed triggers about 16.4MB/s disk write for non duplicates with one backup task.
% [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
% the cloud infrastructure services and are shared among many applications.]
%We see our hybrid deduplication scheme only occupies a small amount of system resources. 
%The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
%memory during duplicate detection.

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of software layers
when I/O throttling is not applied to control usage. The
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
Column ``QFS'' is the write request traffic to the underlying file system after compression.
For example, with 148 MB/s write traffic to the snapshot store, QFS write traffic is about 35.3 MB/s
after compression.  However, the underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46 GB/s 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset, each version of total snapshots has abut 1TB per machine for 25 VMs and  thus  each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
In comparison, the sampled index method in~\cite{Guo2011} achieves about 5.5GB per second
with 16 concurrent backup tasks and 6GB per second with
more tasks.  Thus the per-machine throughput of our scheme is reasonable.
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

@@

We demonstrate  
%the impact of adding extra replication for PDS in VC
%and compare 
the snapshot availability of VC and SRB-based VO  when there are failed machines. 
Appendix~\ref{sect:fault} provides a detailed analysis of 
snapshot availability and the estimated result depends on how frequent a duplicate chunk
is shared among snapshots of VMs.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO 
and VC approaches
and then calculate the average availability of VM snapshots.
